### 2008-12-19 talk/ecoop2009/jitgen.tex
add note to not forget
remove note that we agreed on IRC to ignore

Let us look at an example. Figure \ref{fig:tlc-main} shows parts of the
main-loop of the TLC interpreter (in slightly simplified form). The static
arguments of this functions would typically be the \lstinline{code} argument
(containing the bytecode as a string \anto{what about using array of bytes instead of string? For .NET/JVM people, there is a strong difference between the twos}), the \lstinline{pc} argument (containing
the initial program counter) and the \lstinline{pool} argument (containing the
constant pool). The \lstinline{args} argument is dynamic since it contains the
user-input of the interpreted function. Since the \lstinline{while} loop and the
contained conditions depend only on static arguments it will typically be
unrolled by a partial evaluator.

@@

Promotion is invoked with the use of a hint as well:
\texttt{v2 = hint(v1, promote=True)}.
This hint is a \emph{local} request for \texttt{v2} to be green, without
requiring \texttt{v1} to be green.  Note that this amounts to copying
a red value into a green one, which is not possible in classical
approaches to partial evaluation.  See Section \ref{sec:promotion} for a
complete discussion of promotion.

>>>>

Let us look at an example. Figure \ref{fig:tlc-main} shows parts of the
main-loop of the TLC interpreter (in slightly simplified form). The static
arguments of this functions would typically be the \lstinline{code} argument
(containing the bytecode as a string), the \lstinline{pc} argument (containing
the initial program counter) and the \lstinline{pool} argument (containing the
constant pool). The \lstinline{args} argument is dynamic since it contains the
user-input of the interpreted function. Since the \lstinline{while} loop and the
contained conditions depend only on static arguments it will typically be
unrolled by a partial evaluator.

@@

XXX move this to the promotion section
Promotion is invoked with the use of a hint as well:
\texttt{v2 = hint(v1, promote=True)}.
This hint is a \emph{local} request for \texttt{v2} to be green, without
requiring \texttt{v1} to be green.  Note that this amounts to copying
a red value into a green one, which is not possible in classical
approaches to partial evaluation.  See Section \ref{sec:promotion} for a
complete discussion of promotion.
